---
title: "Food Delivery Time Prediction"
author: "Tria Rahmat Mauludin"
date: "2/25/2022"
output: 
  html_document:
    theme : "cosmo"
    toc : true
    toc_depth : 2
    toc_float : true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)
```
# Introduction

# Objective
- Determine the factor that impact the food delivery time

- Create model for predict/estimate the food delivery time

# Import Library
```{r}
library(dplyr)
library(tidyverse)
library(tidymodels)
```

# Import Data
```{r}
library(readxl)
train_data <- read_excel("./dataset/Data_Train.xlsx")
test_data <- read_excel("./dataset/Data_Test.xlsx")
head(train_data)
```

# Preprocess Data
```{r}
str(train_data)
```
## Location
Find the unique location:
```{r}
unique(train_data$Location)
```

From the result above, we will generalized the location by the city (the words after last comma).

- "Mumbai", "Mumbai CST Area" , "Mumbai Central" -> "Mumbai"

- "Bangalore", "Electronic City", "Marathalli", "Whitefield" -> "Bangalore"

- "India Gate", "Delhi", "Delhi University-GTB Nagar", "Delhi Cantt." , "Timarpur", "Noida" -> 
"Delhi"

- "Gurgoan", "Gurgaon" -> "Gurgaon"

- "Kolkata" -> "Kolkata"

- "Maharashtra", "Pune", "Pune University" -> "Maharashtra"

- "Hyderabad", "Begumpet", "Majestic" -> "Hyderabad"

Then, we will change the type into factor

## Cuisines
```{r}
unique(train_data$Cuisines)[1:10]
```
From result above, one delivery order can contained some types of cuisines. We will doing One-Hot Encoding for every cuisines type.

## Average Cost and Minimum Order
We will remove the string `\u20b9` and `,` in every data then change it to numeric type.

## Rating
We will convert as numeric. If the Rating is `NEW`, `Opening Soon`, `Temporarily Closed`, or `-` we will change to `NA`.

## Votes
We will convert as numeric.

## Reviews

We will convert as numeric.

## Delivery Times

We will remove string ` minutes` then convert it to numeric

# Splitting Data
Splitting data into train_data and validation_data
```{r}
set.seed(100)

splitted <- initial_split(train_data, prop = 0.8, strata = 'Delivery_Time')
splitted
```

# Pipeline Preprocessing using tidymodels
```{r}
# Function to transform Location into City
transform_location <- function(Location){
  if(Location %in% c("Mumbai", "Mumbai CST Area" , "Mumbai Central")){
    return ("Mumbai")
  } else if(Location %in% c("Bangalore", "Electronic City", "Marathalli", "Whitefield")){
    return("Bangalore")
  } else if(Location %in% c("India Gate", "Delhi", "Delhi University-GTB Nagar", "Delhi Cantt." , "Timarpur", "Noida")){
    return("Delhi")
  } else if(Location %in% c("Gurgoan", "Gurgaon")){
    return("Gurgaon")
  } else if(Location %in% c("Maharashtra", "Pune", "Pune University")){
    return("Maharashtra")
  } else if(Location %in% c("Hyderabad", "Begumpet", "Majestic")){
    return("Hyderabad")
  } else if(Location %in% c("Kolkata")){
    return("Kolkata")
  }
}

# Preprocess Pipeline
rec_regression <- recipe(Delivery_Time~., data = training(splitted)) %>% 
  step_select(-Restaurant) %>% 
  step_mutate(
    Location =  word(Location, -1, sep=",") %>% trimws() %>% sapply(function(x) transform_location(x)),
    Average_Cost = gsub('[\u20b9]|,', '', Average_Cost) %>% as.numeric(),
    Minimum_Order = gsub('[\u20b9]|,', '', Minimum_Order) %>% as.numeric(),
    Rating = as.character(Rating) %>% as.numeric(),
    Votes = as.character(Votes) %>% as.numeric(),
    Reviews = as.character(Reviews) %>% as.numeric(),
    Delivery_Time = gsub('[ minutes]', '', Delivery_Time) %>%  as.numeric()
  ) %>% 
  step_dummy_extract(Cuisines, sep= ", ") %>%
  step_naomit(everything()) %>% 
  prep()

rec_classification <- rec_regression %>% 
  step_mutate(Delivery_Time = as.factor(Delivery_Time)) %>% 
  prep()
```

Create training and validation data
```{r}
data_train_reg <- juice(rec_regression)
data_train_cla <- juice(rec_classification)
head(data_train_cla)
```

```{r}
data_validation_reg <- bake(rec_regression, testing(splitted))
data_validation_cla <- bake(rec_classification, testing(splitted))
head(data_validation_reg)
```

Check if there is any `NA` value.
```{r}
any(is.na(data_train_reg))
any(is.na(data_train_cla))
any(is.na(data_validation_reg))
any(is.na(data_validation_cla))
```
# EDA
## Time Distribution over Different Location
```{r}
boxplot(Delivery_Time ~ Location, data = data_train_reg)
```
```{r}
xtabs(~Location+Delivery_Time, data = data_train_reg)
```
## Time Distribution over Rating
```{r}
xtabs(~Rating+Delivery_Time, data = data_train_reg)
```

# Modeling
## Regression Linear Model
```{r}
reg_model <- linear_reg(mode = "regression",
                       engine = "lm") %>%
             fit(formula=Delivery_Time ~ Location + Average_Cost + Minimum_Order + Rating + Votes + Reviews,
                 data=data_train_reg)
summary(reg_model$fit)
```
```{r}
result <- data_validation_reg %>%
  select(Delivery_Time) %>%
  bind_cols(predict(reg_model, new_data = data_validation_reg))
 
library(MLmetrics)
MAPE(result$Delivery_Time, result$.pred)
```

## Multinomial Classification
```{r}
library(nnet)
multi_model <- multinom_reg(mode = "classification",
                            engine = "nnet") %>% 
                fit(formula=Delivery_Time ~ .,
                  data=data_train_cla, size = 10, maxit=100)
```

```{r}
data_validation_cla %>% 
  select(Delivery_Time) %>% 
  bind_cols(predict(multi_model, new_data=data_validation_cla)) %>% 
  accuracy(truth = Delivery_Time, .pred_class)
```
## Random Forest
```{r}
set.seed(190)
rf_model <- rand_forest(mode = "classification", 
                        engine = "ranger",
                        mtry = 10, 
                        trees = 1000) %>% 
            fit(Delivery_Time ~ ., data = data_train_cla)
```

```{r}
data_validation_cla %>% 
  select(Delivery_Time) %>% 
  bind_cols(predict(rf_model, new_data=data_validation_cla)) %>% 
  accuracy(truth = Delivery_Time, .pred_class)
```
# Model Evaluation

# Conclusion

